---
title: "Practical Machine Learning Course Assignment Writeup"
author: "Yiannis"
date: "27 Φεβρουαρίου 2016"
output: html_document
---



The training data for this project are available here: https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here: https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

Import caret package and read the files and import them in your working directory:

```{r,}
library(caret)
library(randomForest)
library(e1071)
url1 <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
download.file(url1, destfile="pmltraining.csv")
url2 <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
download.file(url2, destfile="pmltesting.csv")
training_raw <- read.csv("pmltraining.csv", header=TRUE)
testing_raw <- read.csv("pmltesting.csv", header=TRUE)

```

I keep those variables which are related to sensors (e.g. belt, arm, dumbbell, forearm) and the classe variable as it holds the classification of the activity performed by the user.

Also I discard the variables which have only null values.
```{r}
sensor_col <- grepl("belt|arm|dumbbell|forearm|classe",names(training_raw))
training_set <- training_raw[,sensor_col]
null_col <- colSums(is.na(training_set))!=0
training_set <- training_set[,!null_col]
```

Split of the original training set into two subsets (train 80% and testing 20%) and then use the Random Forest Method to boost Accuracy of the Model


```{r}

set.seed(1234)
training_cv_index <- createDataPartition(training_set$classe,list=FALSE ,p=0.8)
training_cv <- training_set[training_cv_index,]
validation_cv <- training_set[-training_cv_index,]

```


```{r}

model <- train(classe ~., method="rf", data=training_cv, trControl=trainControl(method='cv'), number=5, allowParallel=TRUE )

```

see the results of the model

```{r}

model


```

Model Validation

```{r}

confusionMatrix(validation_cv$classe,predict(model,validation_cv))

```


predict model values

```{r}

result <-predict(model,testing_raw)
result

```


